---
title: "introduction"
author: "Zihan Liu"
date: "2019年5月3日"
output: html_document
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## introduction
This package contains 10 main functions to help calculate different parameters associated with a specified binomial distribution.

## content
The four main functions are:
bin_choose()
bin_probability()
bin_distribution()
bin_cumulative()
bin_variable()
bin_mean()
bin_variance()
bin_mode()
bin_skewness()
bin_kurtosis()

## Function bin_choose()
bin_choose() has a similar function to the algorithm "n choose k," which calculates the number of combinations in which k successes can occur in n trials. It takes in 2 variables: "n"-number of trials (non-negative integer), and "k"-number of successful trials (non-negative integer). It returns the number of combinations in which k successes can occur in n trials. Example:
```{r Function bin_choose()}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```

## Function bin_probability()
bin_probability() calculates the probability of exactly k successes on n repeated trials. It takes in 3 variables: "trials"-number of trials (non-negative integer), "success"-number of successful trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It returns the probability of exactly k successes on n repeated trials. Example:
```{r Function bin_probability()}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
bin_probability(success = 55, trials = 100, prob = 0.45)
```

## Function bin_distribution()
bin_distribution() output a data.frame with two classes: c("bindis", "data.frame"), which describes the probability of k success happening in n trials of a binomial distribution. It takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It returns a data.frame with two classes: c("bindis", "data.frame") outlining probabilities of a binomial distribution. If specified, it also outputs a plot of the corresponding probabilities. Example:
```{r Function bin_distribution()}
bin_distribution(trials = 5, prob = 0.5)
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Function bin_cumulative()
bin_cumulative() output a data.frame with two classes: c("bincum", "data.frame"), which describes the cumulative probability of k success happening in n trials of a binomial distribution. It takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It returns a data.frame with two classes: c("bindis", "data.frame") outlining the cumulative probabilities of a binomial distribution. If specified, it also outputs a plot of the corresponding cumulative probabilities. Example:
```{r Function bin_cumulative()}
bin_cumulative(trials = 5, prob = 0.5)
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

## Function bin_variable()
bin_variable() output a data.frame with two classes: c("bindis", "data.frame"), which describes the parameters used in the binomial distribution. It takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It returns a data.frame with two classes: c("bindis", "data.frame") outlining parameters used in the binomial distribution. If specified, it also outputs other summarizing parameters of the binomial distribution. Example:
```{r Function bin_variable()}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1
```

## Function bin_mean()
bin_mean() takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It calculates the mean of a binomial distribution. Example:
```{r Function bin_mean()}
bin_mean(10, 0.3)
```

## Function bin_variance()
bin_variance() takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It calculates the variance of a binomial distribution. Example:
```{r Function bin_variance()}
bin_variance(10, 0.3)
```

## Function bin_mode()
bin_mode() takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It calculates the mode of a binomial distribution. Example:
```{r Function bin_mode()}
bin_mode(10, 0.3)
```

## Function bin_skewness()
bin_skewness() takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It calculates the skewness of a binomial distribution. Example:
```{r Function bin_skewness()}
bin_skewness(10, 0.3)
```

## Function bin_kurtosis()
bin_kurtosis() takes in 2 variables: "trials"-number of trials (non-negative integer), and "prob"-the probability in which a trial is successful (numeric). It calculates the kurtosis of a binomial distribution. Example:
```{r Function bin_kurtosis()}
bin_kurtosis(10, 0.3)
```
